Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-01 Paper/RSVOptimization.rnw
Preventable fraction plots in supplement

<<tollandOnsetFull, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/tollandOnsetFull", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)

@@

>>>>

<<tollandOnsetFull, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/tollandOnsetFull.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)

@@

<<tollandPredSingle, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/tollandPredSingle.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)

    data = tollandPredSingle

    thresholds = data %>%
    	mutate(ppx=strat(time)) %>%
    	filter(ppx > 0) %>%
    	do((function(df) {
    	  df = df %>% arrange(time)
    		data.frame(
    			ppx.start=min(df$time),
    			ppx.end=max(df$time),
    			unprotected.start=first(df$rsv.cum.frac),
    			unprotected.end=last(df$rsv.cum.frac)
    		)
    	})(.)) %>%
    	ungroup() %>%
    	as.data.frame()

    ggplot(data) +
      theme_light(base_size=plotTextBaseSize) +
      geom_line(aes(x=time, y=rsv.cum.frac, group=sim), color="grey") +
      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
      geom_segment(data=thresholds, aes(x=ppx.start, y=unprotected.start, xend=+Inf, yend=unprotected.start), linetype="11", size=.375) + 
      geom_segment(data=thresholds, aes(x=ppx.end, y=unprotected.end, xend=+Inf, yend=unprotected.end), linetype="11", size=.375) + 
      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac, size=0.5), size=0.5) +
    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=1.75) + 
    	geom_rect(data=thresholds, aes(xmin=max(monthBoundaries$max) - 3, xmax=max(monthBoundaries$max), ymin=unprotected.start, ymax=unprotected.end), size=.375) + 
    	geom_text(data=thresholds, aes(x=max(monthBoundaries$max) - 1.5, y=mean(c(unprotected.start, unprotected.end)), label="$\\Delta$ = preventable fraction", angle=90, lineheight=0.5), color="white", size=1.75) + 
      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, limits=range(c(monthBoundaries$min, monthBoundaries$max)), expand=c(0, 0)) + 
      theme(
        panel.grid.major.x=element_blank(),
        legend.title=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
        legend.position="bottom"
      )

<<tollandPreventableFractionFull, results='hide', warning=FALSE>>=
    tikz(sprintf("%s/tollandPreventableFractionFull.tex", figuresDir), width=pagePlotWidth * 0.4, height=pagePlotHeight, pointsize=10)

    splinePlot = ggplot(data) +
      theme_light(base_size=plotTextBaseSize) +
      geom_line(data=splineData, aes(x=time, y=rsv.cum.frac, group=sim), color="gray") +
      geom_segment(data=thresholds, aes(x=ppx.start, y=-Inf, xend=ppx.start, yend=+Inf), linetype="11", size=.375) + 
      geom_segment(data=thresholds, aes(x=ppx.end, y=-Inf, xend=ppx.end, yend=+Inf), linetype="11", size=.375) + 
    	geom_rect(data=thresholds, aes(xmin=ppx.start, xmax=ppx.end, ymin=1, ymax=1.1), size=.375) + 
    	geom_text(data=thresholds, aes(x=mean(c(ppx.start, ppx.end)), y=1.05, label="Prophylaxis window"), color="white", size=1.75) + 
      geom_point(data=tollandObs, aes(x=time, y=rsv.cum.frac), size=0.5) +
      scale_x_continuous(breaks=monthBoundaries$mid, labels=epiWeekLabels, expand=c(0, 0)) +
      scale_y_continuous() +
      theme(
        panel.grid.major.x=element_blank(),
        legend.title=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
        legend.position="bottom"
      )

    violinPlot <- ggplot(tollandFractionFull) +
      theme_light(base_size=plotTextBaseSize) +
      geom_violin(
        aes(x=0, y=unprotected),
        width=.01,
        fill="gray50", color="black",
        trim=FALSE, draw_quantiles=c(0.025, 0.5, 0.975)
      ) +
      scale_x_continuous() +
      scale_y_continuous(limits=c(0, 1)) +
      theme(
        panel.grid.major.x=element_blank(),
        legend.title=element_blank(),
        axis.title.y=element_blank(),
        axis.ticks.x=element_blank(),
        axis.text.x=element_text(angle=90, hjust=0.5, vjust=0.5),
        legend.position="bottom"
      ) 
    grid.arrange(splinePlot, violinPlot, layout_matrix=rbind(c(rep(1, 4), 2)))

\begin{figure}
\begin{center}
\begin{subfigure}{.4\textwidth}
    \begin{center}
    \input{\figuresDir/tollandPredSingle}
    \caption{Preventable fraction derived from a randomly sampled $P$-spline approximating the RSV time series.}
    \label{fig:tollandPredMini}
    \end{center}
\end{subfigure}
\begin{subfigure}{.4\textwidth}
    \begin{center}
    \input{\figuresDir/tollandPreventableFractionFull}
    \caption{Distribution of approximating $P$-splines ($N=\Sexpr{tollandDisplayNsim}$) and preventable fractions ($N=\Sexpr{tollandNsimFull}$) of RSV under the AAP prophylaxis guidelines  in Tolland county, Connecticut.}
    \label{fig:tollandOnsetMini}
    \end{center}
\end{subfigure}
\end{center}
\caption{Cumulative relative incidence of RSV-associated hospitalizations in Tolland county, Connecticut, with five randomly sampled approximating $P$-splines.}
\end{figure}
